Introducing statistics with \texttt{intRo}

### 2015-11-23 jcgs-paper-2016/paper.Rmd
Move around the modularity stuff

## Extensible
\label{sec:extensible}
On the front end, user interaction with \texttt{intRo} is split into bitesize chunks that we call modules. This is true of the back end as well. Each module is a self contained set of \texttt{R} code that is dynamically added to the application at run time. What this means is that \texttt{intRo} can be easily extended by the addition of modules within the framework underlying the application. This extensibility allows for \texttt{intRo} to be customized for an individual classroom setting, tailored to the needs of a particular course.

@@

## Modules
TODO: Condense this into either a single paragraph, list, and/or table - Move to Extensible section
TODO: Rewrite this as the details behind the modularity. Add information on writing your own modules

Within the set statistics modules, there are three simple statistics tasks that an introductory statistics student will learn in her first semester. The contingency table module allows the user to compute a contingency table for two categorical variables. The results can either be displayed as counts, row percentages, column percentages, or total percentages. The simple linear regression module allows the user to compute a simple linear regression of a dependent variable (y) on an independent variable (x). The module will automatically filter any variables that are non-numeric so that the user may only select variables that are suitable for a simple linear regression. Results of the regression will be displayed on the right. A table of parameter estimates, a scatterplot of the data along with a line of best fit, The R-Squared value, and residual diagnostic plots will all be displayed. A user also has the ability to save residuals and predicted values to their dataset for further analysis. The T test module allows the user to perform either a one variable or two variable Student's T test. The user can select configuration options, including the direction of the test and the confidence level of the test. The results, including the t statistic, degrees of freedom, p-value, and a confidence interval, will be displayed in a text box in the results panel.

>>>>

## Extensible
\label{sec:extensible}
On the front end, user interaction with \texttt{intRo} is split into bitesize chunks that we call modules. Modules are self-contained pieces of functionality which implement common statistical procedures that are often used in introductory statistics classes.

Within the set of statistics modules, there are three simple statistics tasks that an introductory statistics student will learn in her first semester. The contingency table module allows the user to compute a contingency table for two categorical variables. The results can either be displayed as counts, row percentages, column percentages, or total percentages. The simple linear regression module allows the user to compute a simple linear regression of a dependent variable (y) on an independent variable (x). The module will automatically filter any variables that are non-numeric so that the user may only select variables that are suitable for a simple linear regression. Results of the regression will be displayed on the right. A table of parameter estimates, a scatterplot of the data along with a line of best fit, The R-Squared value, and residual diagnostic plots will all be displayed. A user also has the ability to save residuals and predicted values to their dataset for further analysis. The T test module allows the user to perform either a one variable or two variable Student's T test. The user can select configuration options, including the direction of the test and the confidence level of the test. The results, including the t statistic, degrees of freedom, p-value, and a confidence interval, will be displayed in a text box in the results panel.

Each module is a self contained set of \texttt{R} code that is dynamically added to the application at run time. What this means is that \texttt{intRo} can be easily extended by the addition of modules within the framework underlying the application. This extensibility allows for \texttt{intRo} to be customized for an individual classroom setting, tailored to the needs of a particular course.

@@

## Modules
TODO: Rewrite this as the details behind the modularity. Add information on writing your own modules
